Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-04 supplement/06_bat_data.Rmd
use new pal

# prepare a palette
pal <- RColorBrewer::brewer.pal(4, "Set1")
```

@@

# installation using remotes
remotes::install_github("pratikunterwegs/atlastools")
```

>>>>

# prepare a palette
pal <- pals::kovesi.rainbow_bgyr_35_85_c73(3)
```

@@

# installation using remotes
if (!require(remotes)) {
  remotes::install_github("pratikunterwegs/atlastools", upgrade = FALSE)
}
```
